---
title: "Data_Harvesting_Lyrics_ES_DE_TR"
format: 
  html: 
    toc: true
    toc-location: left
    toc-floating: true
    toc-depth: 3  
    number-sections: true  
editor: visual
---

## Introduction / Purpose of Study

The purpose of this project is to showcase data harvesting skills and perform a text mining assignment to reveal violent language use in rap-hiphop songs across German, Turkish and Spanish on the basis of gender.

As the reader is soon to witness, this project will gradually drift apart from the gender violence focus and employ a general sentiment analysis approach. But worry not! This is only because all three languages have done very well and used violent language in the gender context extremely rarely. That is why we asked the following question: Then what do they sing about?

At the early stages of the project, we will be focusing on extracting information regarding the most popular artists and their three most popular songs across Germany, Turkey, and Spain. Having employed Spotify API for that purpose, we will then proceed to extracting lyrics from Genius.com using the Genius API. In doing so, we will not benefit from any packages that are specific to these tasks and use our own functions and scraping methods.

To not spoil all the fun, we will move onto the scraping section.

## Libraries

```{r, message=FALSE}
library(rvest)     
library(stringdist) 
library(httr)      
library(jsonlite)  
library(dplyr)     
library(purrr)     
library(tibble)    
library(tidyr)     
library(stringr)   
library(stopwords) 
library(widyr)     
library(ggplot2)   
library(tidytext)  
library(quanteda) 
library(wordcloud2)


```

```{r}
#| include: false
#usethis::edit_r_environ()

SPOTIFY_CLIENT_ID <- Sys.getenv("SPOTIFY_CLIENT_ID") 
SPOTIFY_CLIENT_SECRET <- Sys.getenv("SPOTIFY_CLIENT_SECRET")

GENIUS_CLIENT_ID <- Sys.getenv("GENIUS_CLIENT_ID")
GENIUS_CLIENT_SECRET <-Sys.getenv("GENIUS_CLIENT_SECRET")

```

## Top 5 German Hip/ Hop Rap Artists & Their Top Songs on Spotify

Authentication: Get Spotify API Token

```{r}
get_spotify_token <- function(client_id, client_secret) {
  auth_url <- "https://accounts.spotify.com/api/token"  
  
  response <- POST(
    auth_url,  
    body = list(
      grant_type = "client_credentials",  
      client_id = SPOTIFY_CLIENT_ID,  
      client_secret = SPOTIFY_CLIENT_SECRET  
    ),
    encode = "form"  
  )
  
  
  if (http_status(response)$category != "Success") {  
    stop("Failed to authenticate. Check your client ID and secret.")  
  }
  
  
  token_data <- content(response, as = "parsed", type = "application/json")  
  
  
  if (!"access_token" %in% names(token_data)) {  
    stop("Error: Could not retrieve access token.")  
  }
  
  return(token_data$access_token)  
}

access_token <- get_spotify_token(SPOTIFY_CLIENT_ID, SPOTIFY_CLIENT_SECRET)  

```

Search for Hip-Hop/Rap Artists from Germany

```{r}
search_artists <- function(query, access_token, limit = 50) {
  Sys.sleep(0.5)  
  
  response <- GET(
    "https://api.spotify.com/v1/search",
    query = list(q = query, type = "artist", limit = limit),
    add_headers(Authorization = paste("Bearer", access_token))
  )
  
  
  if (http_status(response)$category != "Success") {
    message("API request failed for query: ", query)
    return(NULL)  
  }
  
  data <- content(response, as = "parsed", type = "application/json")
  
  
  if (!"artists" %in% names(data) || length(data$artists$items) == 0) {
    message("No artists found for query: ", query)
    return(NULL)
  }
  
  
  tibble(
    id = map_chr(data$artists$items, "id", .default = NA),  
    name = map_chr(data$artists$items, "name", .default = NA),  
    popularity = map_dbl(data$artists$items, "popularity", .default = 0)  
  )
}

search_terms_german <- c("Deutschrap", "Rap Germany", "Deutscher Rapper", "Trap Germany", "Drill Germany",
                         "Hip Hop Germany")


all_artists_german <- map_df(search_terms_german, search_artists, access_token = access_token) %>%
  distinct(id, .keep_all = TRUE) %>%  
  arrange(desc(popularity))  

top_artists_german <- head(all_artists_german, 7)

```

Fetch Detailed Artist Metadata

```{r}

get_artist_details_german <- function(artist_ids, access_token) {
  Sys.sleep(0.5)  
  
  response <- GET(
    "https://api.spotify.com/v1/artists",
    query = list(ids = paste(artist_ids, collapse = ",")),  
    add_headers(Authorization = paste("Bearer", access_token))
  )
  
  
  data <- content(response, as = "parsed")$artists
  
  
  tibble(
    id = map_chr(data, "id"),  
    followers = map_dbl(data, ~ .x$followers$total %||% 0)  
  )
}

artist_details_german <- get_artist_details_german(top_artists_german$id, access_token)

top_artists_german <- left_join(top_artists_german, artist_details_german, by = "id")

```

Retrieve Top Songs for Each Artist

```{r}
get_top_tracks <- function(artist_id, access_token) {
  Sys.sleep(0.5)  
  
  response <- GET(
    paste0("https://api.spotify.com/v1/artists/", artist_id, "/top-tracks"),
    query = list(market = "DE"),  
    add_headers(Authorization = paste("Bearer", access_token))
  )
  
  tracks_data <- content(response, as = "parsed")$tracks
  
  if (length(tracks_data) == 0) {
    return(tibble(track_name = NA_character_, track_popularity = NA_real_))
  }
  
  tibble(
    track_name = map_chr(tracks_data[1:5], "name", .default = NA),  
    track_popularity = map_dbl(tracks_data[1:5], "popularity", .default = NA)   
  )
}

top_artists_german <- top_artists_german %>%
  mutate(top_tracks = map(id, ~ get_top_tracks(.x, access_token)))

```

Clean and Format the Final Results

```{r}

top_artists_german_tracks <- top_artists_german %>%
  select(artist_name = name, artist_popularity = popularity, 
         followers, top_tracks) %>%
  unnest(cols = top_tracks)


top_artists_german_tracks <- top_artists_german_tracks %>%
  filter(!artist_name %in% c("Morad", "Rvfv"))


print(top_artists_german_tracks)


```

## Top 5 Turkish Hip/ Hop Rap Artists & Their Top Songs on Spotify

authentication: Get Spotify API Token

```{r}


get_spotify_token <- function(client_id, client_secret) {
  auth_url <- "https://accounts.spotify.com/api/token"  
  
  response <- POST(
    auth_url,
    body = list(
      grant_type = "client_credentials",  
      client_id = SPOTIFY_CLIENT_ID, 
      client_secret = SPOTIFY_CLIENT_SECRET
    ),
    encode = "form"
  )
  
  if (http_status(response)$category != "Success") {
    stop("Failed to authenticate. Check your client ID and secret.")
  }
  
  token_data <- content(response, as = "parsed", type = "application/json")
  
  if (!"access_token" %in% names(token_data)) {
    stop("Error: Could not retrieve access token.")
  }
  
  return(token_data$access_token)  
}

access_token <- get_spotify_token(SPOTIFY_CLIENT_ID, SPOTIFY_CLIENT_SECRET)  

```

Search for Hip-Hop/Rap Artists from Turkey

authentication: Get Spotify API Token

```{r}
get_spotify_token <- function(client_id, client_secret) {
  auth_url <- "https://accounts.spotify.com/api/token"  
  
  response <- POST(
    auth_url,  
    body = list(
      grant_type = "client_credentials",  
      client_id = SPOTIFY_CLIENT_ID,  
      client_secret = SPOTIFY_CLIENT_SECRET  
    ),
    encode = "form" 
  )

  if (http_status(response)$category != "Success") {  
    stop("Failed to authenticate. Check your client ID and secret.")  
  }

  token_data <- content(response, as = "parsed", type = "application/json")  
  
  if (!"access_token" %in% names(token_data)) {  
    stop("Error: Could not retrieve access token.")  
  }

  return(token_data$access_token)  
}
access_token <- get_spotify_token(client_id, client_secret) 
```

Search for Hip-Hop/Rap Artists from Turkey

```{r}
search_artists <- function(query, access_token, limit = 50) {
  Sys.sleep(0.5)  

  response <- GET(
    "https://api.spotify.com/v1/search",  
    query = list(q = query, type = "artist", limit = limit),  
    add_headers(Authorization = paste("Bearer", access_token))  
  )

  if (http_status(response)$category != "Success") {  
    message("API request failed for query: ", query)  
    return(NULL)  
  }

  data <- content(response, as = "parsed", type = "application/json")  

  if (!"artists" %in% names(data) || length(data$artists$items) == 0) {  
    message("No artists found for query: ", query)  
    return(NULL)  
  }

  
  tibble(
    id = map_chr(data$artists$items, "id", .default = NA),  
    name = map_chr(data$artists$items, "name", .default = NA),  
    popularity = map_dbl(data$artists$items, "popularity", .default = 0)  
  )
}

search_terms <- c("hip hop Türkiye", "rap Türkiye", "trap Türkiye", "drill Türkiye",  
                  "alternatif rap Türkiye", "gangsta rap Türkiye", "hip hop underground Türkiye", "old school hip hop Türkiye")

all_artists <- map_df(search_terms, search_artists, access_token = access_token) %>%  
  distinct(id, .keep_all = TRUE) %>%  
  arrange(desc(popularity))  
top_artists <- head(all_artists, 5)  

```

Fetch Detailed Artist Metadata

```{r}
get_artist_details <- function(artist_ids, access_token) {
  Sys.sleep(0.5)  

  response <- GET(
    "https://api.spotify.com/v1/artists",  
    query = list(ids = paste(artist_ids, collapse = ",")),  
    add_headers(Authorization = paste("Bearer", access_token))  
  )

  
  data <- content(response, as = "parsed")$artists  

  tibble(
    id = map_chr(data, "id"),  
    followers = map_dbl(data, ~ .x$followers$total %||% 0)  
  )
}


artist_details <- get_artist_details(top_artists$id, access_token)  

top_artists <- left_join(top_artists, artist_details, by = "id")  


```

Retrieve Top 3 Songs for Each Artist

```{r}
get_top_tracks <- function(artist_id, access_token) {
  Sys.sleep(0.5)  

  response <- GET(
    paste0("https://api.spotify.com/v1/artists/", artist_id, "/top-tracks"),  
    query = list(market = "TR"),  
    add_headers(Authorization = paste("Bearer", access_token))  
  )

  tracks_data <- content(response, as = "parsed")$tracks  

  if (length(tracks_data) == 0) {
    return(tibble(track_name = NA_character_, track_popularity = NA_real_))   
  }

  tibble(
    track_name = map_chr(tracks_data[1:3], "name", .default = NA),  
    track_popularity = map_dbl(tracks_data[1:3], "popularity", .default = NA)  
  )
}

top_artists <- top_artists %>%
  mutate(top_tracks = map(id, ~ get_top_tracks(.x, access_token)))  

```

Clean and Format the Final Results

```{r}

top_artists_tracks <- top_artists %>%
  select(artist_name = name, artist_popularity = popularity,  
         followers, top_tracks) %>%  
  unnest(cols = top_tracks)  

print(top_artists_tracks)  
```

## Top 5 Spanish Artists

```{r}

get_spotify_token <- function(client_id, client_secret) {
  auth_url <- "https://accounts.spotify.com/api/token"  
  
  response <- POST(
    auth_url,
    body = list(
      grant_type = "client_credentials",  
      client_id = SPOTIFY_CLIENT_ID, 
      client_secret = SPOTIFY_CLIENT_SECRET
    ),
    encode = "form"
  )
  
  if (http_status(response)$category != "Success") {
    stop("Failed to authenticate. Check your client ID and secret.")
  }
  
  token_data <- content(response, as = "parsed", type = "application/json")
  
  if (!"access_token" %in% names(token_data)) {
    stop("Error: Could not retrieve access token.")
  }
  
  return(token_data$access_token)  
}

access_token <- get_spotify_token(SPOTIFY_CLIENT_ID, SPOTIFY_CLIENT_SECRET)  

```

Search for Hip-Hop/Rap Artists from Spain

```{r}
search_artists_es <- function(query, access_token, limit = 50) {
  Sys.sleep(0.5)  
  
  response <- GET(
    "https://api.spotify.com/v1/search",
    query = list(q = query, type = "artist", limit = limit),
    add_headers(Authorization = paste("Bearer", access_token))
  )
  
  if (http_status(response)$category != "Success") {
    message("API request failed for query: ", query)
    return(NULL)  
  }
  
  data <- content(response, as = "parsed", type = "application/json")
  
  if (!"artists" %in% names(data) || length(data$artists$items) == 0) {
    message("No artists found for query: ", query)
    return(NULL)
  }
  
  tibble(
    id = map_chr(data$artists$items, "id", .default = NA),  
    name = map_chr(data$artists$items, "name", .default = NA),  
    popularity = map_dbl(data$artists$items, "popularity", .default = 0)  
  )
}

search_terms_es <- c("hip hop España", "rap España", "trap España", "drill España",
                     "rap alternativo España", "rap consciente España", 
                     "gangsta rap España", "hip hop underground España", 
                     "latin trap España", "reggaeton España", 
                     "música urbana España", "old school hip hop España",
                     "spanglish hip hop España")

all_artists_es <- map_df(search_terms_es, search_artists_es, access_token = access_token) %>%
  distinct(id, .keep_all = TRUE) %>%  
  arrange(desc(popularity))  

top_artists_es <- head(all_artists_es, 5)

```

Fetch Detailed Artist Metadata

```{r}

get_artist_details_es <- function(artist_ids, access_token) {
  Sys.sleep(0.5)  
  
  response <- GET(
    "https://api.spotify.com/v1/artists",
    query = list(ids = paste(artist_ids, collapse = ",")),  
    add_headers(Authorization = paste("Bearer", access_token))
  )
  
  data_es <- content(response, as = "parsed")$artists
  
  tibble(
    id = map_chr(data_es, "id"),  # Artist ID
    followers = map_dbl(data_es, ~ .x$followers$total %||% 0)  
  )
}

artist_details_es <- get_artist_details_es(top_artists_es$id, access_token)

top_artists_es <- left_join(top_artists_es, artist_details_es, by = "id")  

```

Retrieve Top 3 Songs for Each Artist

```{r}
get_top_tracks_es <- function(artist_id, access_token, existing_songs = NULL) {
  Sys.sleep(0.5)
  
  response_es <- GET(
    paste0("https://api.spotify.com/v1/artists/", artist_id, "/top-tracks"),
    query = list(market = "ES"),
    add_headers(Authorization = paste("Bearer", access_token))
  )
  
  if (status_code(response_es) != 200) {
    message(paste("API request failed for artist ID:", artist_id, "Status:", status_code(response_es)))
    return(tibble(track_name_es = NA_character_, track_popularity_es = NA_real_))
  }
  
  parsed_response <- content(response_es, as = "parsed", type = "application/json")
  
  if (!"tracks" %in% names(parsed_response) || length(parsed_response$tracks) == 0) {
    message(paste("No tracks found for artist ID:", artist_id))
    return(tibble(track_name_es = NA_character_, track_popularity_es = NA_real_))
  }
  
  tracks_data_es <- parsed_response$tracks
  
  tracks_df_es <- tibble(
    track_name_es = map_chr(tracks_data_es, "name", .default = NA),
    track_popularity_es = map_dbl(tracks_data_es, "popularity", .default = NA)
  ) %>%
    arrange(desc(track_popularity_es))  
  
  if (!is.null(existing_songs)) {
    tracks_df_es <- tracks_df_es %>% filter(!(track_name_es %in% existing_songs))
  }
  
  return(head(tracks_df_es, min(nrow(tracks_df_es), 3)))
}

selected_songs_es <- c()

top_artists_es <- top_artists_es %>%
  mutate(top_tracks_es = map(id, ~ {
    tracks <- get_top_tracks_es(.x, access_token, existing_songs = selected_songs_es)
    selected_songs_es <<- c(selected_songs_es, tracks$track_name_es) 
    return(tracks)
  }))

```

Clean and Format the Final Results

```{r}
top_artists_tracks_es <- top_artists_es %>%
  select(artist_name = name, artist_popularity = popularity, 
         followers, top_tracks_es) %>%  
  unnest(cols = top_tracks_es)

print(top_artists_tracks_es)

```

### Get the Lyrics German

We will try to extract Genius IDs for songs on top of the URL

```{r}

get_genius_token <- function(client_id, client_secret) {
  response <- POST(
    "https://api.genius.com/oauth/token",
    body = list(
      grant_type = "client_credentials",
      client_id = GENIUS_CLIENT_ID,
      client_secret = GENIUS_CLIENT_SECRET
    ),
    encode = "form"
  )
  if (status_code(response) != 200) {
    stop("Oops! Can’t get a new card. Check your ID and secret.")
  }
  data <- content(response, as = "parsed", type = "application/json")
  return(data$access_token)
}

genius_access_token <- get_genius_token(GENIUS_CLIENT_ID, GENIUS_CLIENT_SECRET)

genius_base_url <- "https://api.genius.com"

genious_get_song_data <- function(artist, track, access_token) {
  Sys.sleep(1)  
  
  query <- paste(artist, track, "German", sep = " ")
  search_url <- paste0(genius_base_url, "/search")
  
  response <- GET(
    search_url,
    query = list(q = query, access_token = access_token),
    add_headers("User-Agent" = "Mozilla/5.0")
  )
  
  if (status_code(response) != 200) {
    message(paste("Search failed for:", artist, "-", track, "Status:", status_code(response)))
    return(list(url = NA, id = NA))
  }
  
  data <- content(response, as = "parsed", type = "application/json")
  hits <- data$response$hits
  
  if (length(hits) == 0) {
    message(paste("No Genius match found for:", artist, "-", track))
    return(list(url = NA, id = NA))
  }
  
  similarity <- function(a, b) stringdist(tolower(a), tolower(b), method = "lv")
  
  best_match <- NULL
  best_score <- Inf
  
  for (hit in hits) {
    song <- hit$result
    song_artist <- song$primary_artist$name
    song_title <- song$title
    song_url <- song$url
    song_id <- song$id
    
    if (!grepl("-lyrics$", song_url)) next
    
    artist_similarity <- similarity(artist, song_artist)
    track_similarity <- similarity(track, song_title)
    total_score <- artist_similarity + track_similarity
    
    if (total_score < best_score) {
      best_score <- total_score
      best_match <- list(url = song_url, id = song_id)
    }
    
    if (artist_similarity == 0 && track_similarity == 0) {
      message(paste("Found exact match Genius URL:", song_url))
      return(list(url = song_url, id = song_id))
    }
  }
  
  if (!is.null(best_match)) {
    message(paste("Found best match Genius URL:", best_match$url))
    return(best_match)
  }
  
  message(paste("No suitable match found for:", artist, "-", track))
  return(list(url = NA, id = NA))
}

top_artists_german_tracks <- top_artists_german_tracks %>%
  mutate(
    genius_data = map2(artist_name, track_name, ~ genious_get_song_data(.x, .y, genius_access_token)),
    genius_url = map_chr(genius_data, "url"),
    genius_id = map_int(genius_data, "id")
  ) %>%
  drop_na()

print(top_artists_german_tracks %>% select(artist_name, track_name, genius_url, genius_id))



```

#### Scrape from Genius German

Function to Scrape Lyrics from Genius

```{r}
get_genius_lyrics <- function(song_url) {
  if (is.na(song_url)) return(NA)  
  
  Sys.sleep(1)  
  
  tryCatch({
    page <- read_html(song_url)
    
    lyrics <- page %>%
      html_nodes("div.lyrics") %>%  
      html_text(trim = TRUE)
    
    if (length(lyrics) == 0) {
      lyrics <- page %>%
        html_nodes("div[class^='Lyrics__Container']") %>%
        html_text(trim = TRUE) %>%
        paste(collapse = " ")
    }
    
    if (length(lyrics) == 0) {
      message(paste("Lyrics not found for:", song_url))
      return(NA)
    }
    
    return(lyrics)
  }, error = function(e) {
    message(paste("Error scraping lyrics for:", song_url))
    return(NA)
  })
}


top_artists_german_tracks <- top_artists_german_tracks %>%
  mutate(lyrics  = map_chr(genius_url , get_genius_lyrics ))

```

View and Save Final Dataset

```{r}
print(top_artists_german_tracks  %>% select(artist_name, track_name , genius_url , genius_id , lyrics ))

top_artists_german_tracks_atomic <- top_artists_german_tracks  %>%
  select(artist_name, track_name , genius_url , genius_id , lyrics ) %>%
  mutate(across(everything(), as.character))  
write.csv(top_artists_german_tracks_atomic, "german_artists_lyrics.csv", row.names = FALSE)


```

## Get the Lyrics - Turkish

```{r}
get_genius_token <- function(client_id, client_secret) {
  response <- POST(
    "https://api.genius.com/oauth/token",
    body = list(
      grant_type = "client_credentials",
      client_id = GENIUS_CLIENT_ID,
      client_secret = GENIUS_CLIENT_SECRET
    ),
    encode = "form"
  )
  if (status_code(response) != 200) {
    stop("Oops! Can’t get a new card. Check your ID and secret.")
  }
  data <- content(response, as = "parsed", type = "application/json")
  return(data$access_token)
}

# Get the new token
genius_access_token <- get_genius_token(GENIUS_CLIENT_ID, GENIUS_CLIENT_SECRET)
genius_base_url <- "https://api.genius.com"

# Function to search for a song on Genius and get its URL
get_genius_song_url <- function(artist, track, access_token) {
  Sys.sleep(1)  # Delay to avoid rate limiting
  
  # Construct search query with a hint for Turkish context
  query <- paste(artist, track, "Türkiye", sep = " ")
  search_url <- paste0(genius_base_url, "/search")
  
  # Make the API request
  response <- GET(
    search_url,
    query = list(q = query, access_token = access_token),
    add_headers("User-Agent" = "Mozilla/5.0")
  )
  
  # Check if request was successful
  if (status_code(response) != 200) {
    message(paste("Search failed for:", artist, "-", track, "Status:", status_code(response)))
    return(NA)
  }
  
  # Parse JSON response
  data <- content(response, as = "parsed", type = "application/json")
  hits <- data$response$hits
  
  # Check if any results were found
  if (length(hits) == 0) {
    message(paste("No Genius match found for:", artist, "-", track))
    return(NA)
  }
  
  # Function to calculate string similarity (lower is better)
  similarity <- function(a, b) stringdist(tolower(a), tolower(b), method = "lv")
  
  # Find the best match based on artist and track name
  best_match <- NULL
  best_score <- Inf
  
  for (hit in hits) {
    song <- hit$result
    song_artist <- song$primary_artist$name
    song_title <- song$title
    song_url <- song$url
    
    # Skip if not a lyrics page
    if (!grepl("-lyrics$", song_url)) next
    
    # Calculate similarity scores
    artist_similarity <- similarity(artist, song_artist)
    track_similarity <- similarity(track, song_title)
    total_score <- artist_similarity + track_similarity
    
    # Update best match if this score is lower (better)
    if (total_score < best_score) {
      best_score <- total_score
      best_match <- song_url
    }
    
    # Early exit if exact match found (optional optimization)
    if (artist_similarity == 0 && track_similarity == 0) {
      message(paste("Found exact match Genius URL:", song_url))
      return(song_url)
    }
  }
  
  # Return the best match if found
  if (!is.null(best_match)) {
    message(paste("Found best match Genius URL:", best_match))
    return(best_match)
  }
  
  message(paste("No suitable match found for:", artist, "-", track))
  return(NA)
}

# Add Genius URLs to the dataframe
top_artists_tracks <- top_artists_tracks %>%
  mutate(
    genius_url = map2_chr(artist_name, track_name, ~ get_genius_song_url(.x, .y, genius_access_token))
  )

# View the results
print(top_artists_tracks %>% select(artist_name, track_name, genius_url))
```

```{r}
# Function to search for a song on Genius and get its URL and ID
genious_base_url <- "https://api.genius.com"

get_genius_song_url <- function(artist, track, access_token) {
  Sys.sleep(1)  # Delay to avoid rate limiting
  
  # Construct search query with a hint for Turkish context
  query <- paste(artist, track, "Türkiye", sep = " ")
  search_url <- paste0(genious_base_url, "/search")
  
  # Make the API request
  response <- GET(
    search_url,
    query = list(q = query, access_token = access_token),
    add_headers("User-Agent" = "Mozilla/5.0")
  )
  
  # Check if request was successful
  if (status_code(response) != 200) {
    message(paste("Search failed for:", artist, "-", track, "Status:", status_code(response)))
    return(list(url = NA, id = NA))
  }
  
  # Parse JSON response
  data <- content(response, as = "parsed", type = "application/json")
  hits <- data$response$hits
  
  # Check if any results were found
  if (length(hits) == 0) {
    message(paste("No Genius match found for:", artist, "-", track))
    return(list(url = NA, id = NA))
  }
  
  # Function to calculate string similarity (lower is better)
  similarity <- function(a, b) stringdist(tolower(a), tolower(b), method = "lv")
  
  # Find the best match based on artist and track name
  best_match <- NULL
  best_score <- Inf
  
  for (hit in hits) {
    song <- hit$result
    song_artist <- song$primary_artist$name
    song_title <- song$title
    song_url <- song$url
    song_id <- song$id
    
    # Skip if not a lyrics page
    if (!grepl("-lyrics$", song_url)) next
    
    # Calculate similarity scores
    artist_similarity <- similarity(artist, song_artist)
    track_similarity <- similarity(track, song_title)
    total_score <- artist_similarity + track_similarity
    
    # Update best match if this score is lower (better)
    if (total_score < best_score) {
      best_score <- total_score
      best_match <- list(url = song_url, id = song_id)
    }
    
    # Early exit if exact match found (optional optimization)
    if (artist_similarity == 0 && track_similarity == 0) {
      message(paste("Found exact match Genius URL:", song_url))
      return(list(url = song_url, id = song_id))
    }
  }
  
  # Return the best match if found
  if (!is.null(best_match)) {
    message(paste("Found best match Genius URL:", best_match$url))
    return(best_match)
  }
  
  message(paste("No suitable match found for:", artist, "-", track))
  return(list(url = NA, id = NA))
}

# Add Genius URLs to the dataframe
top_artists_tracks <- top_artists_tracks %>%
  mutate(
    genius_data = map2(artist_name, track_name, ~ get_genius_song_url(.x, .y, genius_access_token)),
    genius_url = map_chr(genius_data, "url"),
    genius_id = map_int(genius_data, "id")
  )

# View the results
print(top_artists_tracks %>% select(artist_name, track_name, genius_url, genius_id))
```

##\$ Get the Lyrics

We will try to extract Genius IDs for songs on top of the URL

```{r}
get_genius_lyrics <- function(song_url) {
  if (is.na(song_url)) return(NA)  # If no URL found, return NA
  
  Sys.sleep(1)  # Pause to avoid getting blocked
  
  # Try reading the page
  tryCatch({
    page <- read_html(song_url)
    
    # Extract lyrics (Genius structure may change, so check elements)
    lyrics <- page %>%
      html_nodes("div.lyrics") %>%  # Old structure
      html_text(trim = TRUE)
    
    # Alternative extraction (new Genius layout)
    if (length(lyrics) == 0) {
      lyrics <- page %>%
        html_nodes("div[class^='Lyrics__Container']") %>%
        html_text(trim = TRUE) %>%
        paste(collapse = " ")
    }
    
    if (length(lyrics) == 0) {
      message(paste("Lyrics not found for:", song_url))
      return(NA)
    }
    
    return(lyrics)
  }, error = function(e) {
    message(paste("Error scraping lyrics for:", song_url))
    return(NA)
  })
}

# Scrape Lyrics for All Songs
top_artists_tracks <- top_artists_tracks %>%
  mutate(lyrics = map_chr(genius_url, get_genius_lyrics))



# View final dataset with Genius IDs, URLs, and Lyrics
print(top_artists_tracks %>% select(artist_name, track_name, genius_url, genius_id, lyrics))

# Ensure all columns are atomic types before saving to CSV
top_artists_tracks_tr_atomic <- top_artists_tracks %>%
  select(artist_name, track_name, genius_url, genius_id, lyrics) %>%
  mutate(across(everything(), as.character))  # Convert all columns to character

```

```{r}

write.csv(top_artists_tracks_tr_atomic, "top_artists_tracks_with_TR.csv", row.names = FALSE)
```

## Get the Lyrics Spanish

Set Up Genius API

```{r}

get_genius_token_es <- function(client_id, client_secret) {
  auth_url <- "https://api.genius.com/oauth/token"
  
  response <- POST(
    auth_url,
    body = list(
      grant_type = "client_credentials",
      client_id = GENIUS_CLIENT_ID,
      client_secret = GENIUS_CLIENT_SECRET
    ),
    encode = "form"
  )
  
  if (http_status(response)$category != "Success") {
    stop("Failed to authenticate with Genius API. Check your client ID and secret.")
  }
  
  token_data <- fromJSON(rawToChar(response$content))
  
  if (!"access_token" %in% names(token_data)) {
    stop("Error: Could not retrieve Genius access token.")
  }
  
  return(token_data$access_token)
}

genius_access_token_es <- get_genius_token_es(GENIUS_CLIENT_ID, GENIUS_CLIENT_SECRET)

genius_base_url_es <- "https://api.genius.com"

```

### Function to Search for a Song on Genius

```{r}
get_genius_song_data_es <- function(artist, track, access_token) {
  Sys.sleep(1)  
  
  query <- paste(artist, track, sep = " ")
  search_url <- paste0(genius_base_url_es, "/search")
  
  response <- GET(
    search_url,
    query = list(q = query, access_token = access_token),
    add_headers("User-Agent" = "Mozilla/5.0")
  )
  
  if (status_code(response) != 200) {
    message(paste("Search failed for:", artist, "-", track, "Status:", status_code(response)))
    return(list(url = NA, id = NA))
  }
  
  data_es <- content(response, as = "parsed", type = "application/json")
  hits_es <- data_es$response$hits
  
  if (length(hits_es) == 0) {
    message(paste("No Genius match found for:", artist, "-", track))
    return(list(url = NA, id = NA))
  }
  
  similarity <- function(a, b) stringdist(tolower(a), tolower(b), method = "lv")
  
  best_match <- NULL
  best_score <- Inf
  
  for (hit in hits_es) {
    song <- hit$result
    song_artist <- song$primary_artist$name
    song_title <- song$title
    song_url <- song$url
    song_id <- song$id
    
    if (!grepl("-lyrics$", song_url)) next
    
    artist_similarity <- similarity(artist, song_artist)
    track_similarity <- similarity(track, song_title)
    total_score <- artist_similarity + track_similarity
    
    if (total_score < best_score) {
      best_score <- total_score
      best_match <- list(url = song_url, id = song_id)
    }
    
    if (artist_similarity == 0 && track_similarity == 0) {
      message(paste("Found exact match Genius URL:", song_url))
      return(list(url = song_url, id = song_id))
    }
  }
  
  if (!is.null(best_match)) {
    message(paste("Found best match Genius URL:", best_match$url))
    return(best_match)
  }
  
  message(paste("No suitable match found for:", artist, "-", track))
  return(list(url = NA, id = NA))
}

```

### Add Genius URLs & IDs to top_artists_tracks_es

```{r}
top_artists_tracks_es <- top_artists_tracks_es %>%
  mutate(
    genius_data_es = map2(artist_name, track_name_es, ~ get_genius_song_data_es(.x, .y, genius_access_token_es)),
    genius_url_es = map_chr(genius_data_es, "url"),
    genius_id_es = map_int(genius_data_es, "id")
  )

```

### Function to Scrape Lyrics from Genius

```{r}
get_genius_lyrics_es <- function(song_url) {
  if (is.na(song_url)) return(NA)  
  
  Sys.sleep(1)  
  
  tryCatch({
    page <- read_html(song_url)
    
    lyrics <- page %>%
      html_nodes("div.lyrics") %>%  
      html_text(trim = TRUE)
    
    if (length(lyrics) == 0) {
      lyrics <- page %>%
        html_nodes("div[class^='Lyrics__Container']") %>%
        html_text(trim = TRUE) %>%
        paste(collapse = " ")
    }
    
    if (length(lyrics) == 0) {
      message(paste("Lyrics not found for:", song_url))
      return(NA)
    }
    
    return(lyrics)
  }, error = function(e) {
    message(paste("Error scraping lyrics for:", song_url))
    return(NA)
  })
}

```

### Scrape Lyrics for All Songs

```{r}
# Scrape Lyrics for All Songs
top_artists_tracks_es <- top_artists_tracks_es %>%
  mutate(lyrics_es = map_chr(genius_url_es, get_genius_lyrics_es))

```

### View and Save Final Dataset

```{r}
print(top_artists_tracks_es %>% select(artist_name, track_name_es, genius_url_es, genius_id_es, lyrics_es))

top_artists_tracks_es_atomic <- top_artists_tracks_es %>%
  select(artist_name, track_name_es, genius_url_es, genius_id_es, lyrics_es) %>%
  mutate(across(everything(), as.character))  

write.csv(top_artists_tracks_es_atomic, "spanish_artists_lyrics.csv", row.names = FALSE)


```

## Cleaning Data

```{r}
turkish_lyrics <- read.csv("top_artists_tracks_with_TR.csv")
```

```{r}
german_lyrics <- read.csv("german_artists_lyrics.csv")
```

cleaning lyrics:

```{r}
clean_lyrics_de <- function(lyrics) {
  if (is.na(lyrics)) return(NA)
  lyrics <- str_replace_all(lyrics, "\\[.*?\\]", "")
  lyrics <- str_replace_all(lyrics, "\\(.*?\\)", "")
  lyrics <- str_replace_all(lyrics, "[^A-Za-z0-9äöüÄÖÜß\\s\\n.,?!;:'\"-]", "")
  lyrics <- str_replace_all(lyrics, "(?<=[a-z0-9])(?=[A-ZÄÖÜ])", "\n")
  lyrics <- str_squish(lyrics)
  
  return(lyrics)
}

```

```{r}
german_lyrics <- german_lyrics %>%
  mutate(cleaned_lyrics = map_chr(lyrics, clean_lyrics_de))

print(german_lyrics %>% select(artist_name, track_name, cleaned_lyrics))

```

Some lyrics are in english or spanish lyrics from german speaking artist, we need to remove those songs:

```{r, echo=FALSE}

german_lyrics <- german_lyrics %>%
  filter(!track_name %in% c( "Cold as Ice", "Toyota (2016)", "Palmen aus Plastik", "Toto (feat. RAF Camora)","04:30","Babylon"))


```

cleaning Turkish lyrics:

```{r}
clean_lyrics_tr <- function(lyrics) {
  if (is.na(lyrics)) return(NA)
  
  
  lyrics <- str_replace_all(lyrics, "\\[.*?\\]", "")  # Remove content within []
  
  lyrics <- str_replace_all(lyrics, "\\(.*?\\)", "")  # Remove content within ()
  
  lyrics <- str_replace_all(lyrics, "\\{.*?\\}", "")  # Remove content within {}
  
  lyrics <- str_replace_all(lyrics, "(?<=[a-z0-9])(?=[A-Z])", "\n")
  
  lyrics <- str_replace_all(lyrics, "[\"'\\?\\\\(),]", "")
  
  lyrics <- str_replace_all(lyrics, "\\s+", " ")
  lyrics <- str_replace_all(lyrics, "(?<!\n)\\s*(?=\n)", "")
  
  lyrics <- str_replace_all(lyrics, "[^A-Za-z0-9ıöüçğşİÖÜÇĞŞ\\s\\n.,?!;:'\"-]", "")
  
  lyrics <- str_squish(lyrics)
  
  return(lyrics)
}

top_artists_tracks_tr_atomic <- top_artists_tracks_tr_atomic %>%
  mutate(lyrics = map_chr(lyrics, clean_lyrics_tr))

print(top_artists_tracks_tr_atomic %>% select(artist_name, track_name, lyrics))

```

```{r}
write.csv(top_artists_tracks_tr_atomic, file = "top_artists_tracks_with_TR.csv", row.names = FALSE)
```

```{r}

# to clean lyrics, because they had weird signs and stuff
cleaned_lyrics_es <- function(lyrics) {
  if (is.na(lyrics)) return(NA)
  
  lyrics <- str_replace_all(lyrics, "\\s*\\[.*?\\]\\s*", " ")
  lyrics <- str_replace_all(lyrics, "\\s*\\(.*?\\)\\s*", " ")
  
  lyrics <- str_replace_all(lyrics, "(?<=[a-z0-9])(?=[A-Z])", "\n")
  
  lyrics <- str_replace_all(lyrics, "\\s+", " ")
  lyrics <- str_replace_all(lyrics, "(?<!\n)\\s*(?=\n)", "")
  
  lyrics <- str_replace_all(lyrics, "[^A-Za-z0-9\\s\\n\\.,?!;:'\"-]", "")
  
  lyrics <- str_squish(lyrics)
  
  return(lyrics)
}

if (!"lyrics_es" %in% colnames(top_artists_tracks_es)) {
  message("Warning: `lyrics_es` column is missing! Initializing as NA.")
  top_artists_tracks_es <- top_artists_tracks_es %>%
    mutate(lyrics_es = NA_character_)
}

top_artists_tracks_es <- top_artists_tracks_es %>%
  mutate(lyrics_es = map_chr(lyrics_es, ~ ifelse(is.na(.x), NA_character_, cleaned_lyrics_es(.x))))

print(top_artists_tracks_es %>% select(artist_name, track_name_es, lyrics_es))

write.csv(top_artists_tracks_es %>% select(artist_name, track_name_es, genius_url_es, genius_id_es, lyrics_es),
          "cleaned_spanish_lyrics.csv", row.names = FALSE)

```

```{r}
spanish_lyrics <- read.csv("cleaned_spanish_lyrics.csv", stringsAsFactors = FALSE)

```

## Text Mining

### Tokenizing the Lyrics & Adding Stopwords

#### German

```{r}
german_lyrics_cleaned <- german_lyrics %>%
  unnest_tokens(word, cleaned_lyrics)

```

```{r}
german_stopwords <- stopwords("de", source = "stopwords-iso")

german_lyrics_cleaned <- german_lyrics_cleaned %>%
  filter(!word %in% german_stopwords)



```

#### Turkish

```{r}

turkish_stops <- stopwords("turkish", source = "stopwords-iso")

```

```{r}
tokens_lyrics_tr <- tokens(top_artists_tracks_tr_atomic$lyrics)
dfm_text <- dfm(tokens_lyrics_tr)

```

#### Spanish

```{r}
# Load standard Spanish stopwords
spanish_stops <- stopwords("es")  

# **Custom stopwords: Add all manually identified words**
custom_stopwords <- c("si", "ah", "oh", "ala", "eh", "verso", "estribillo", "pa", 
                      "quiere", "quiero", "woh", "morad", "sé", "uh", "pone", "ser",
                      "doy", "t'u", "s'e", "vo'a", "jc", "to", "ere", "ahah", "voa", "beny", "yan")  

# **Combine standard + custom stopwords**
all_stopwords <- unique(c(spanish_stops, custom_stopwords))

# **Tokenize, remove stopwords, and count word frequency**
word_freq_es <- top_artists_tracks_es_atomic %>%
  filter(!is.na(lyrics_es) & lyrics_es != "") %>%  # Remove NA + empty rows
  unnest_tokens(word, lyrics_es) %>%  # Tokenize text
  filter(!word %in% all_stopwords & word != "") %>%  # **Remove stopwords**
  count(word, sort = TRUE)  # Count word frequencies

# **Check the result**
print(word_freq_es)

```

### German Word Frequencies & Sentiment Analysis

#### Frequencies 

```{r}
#| include: false
word_freq <- german_lyrics_cleaned %>%
  count(word, sort = TRUE)

word_freq
```

#### Bing-Sentiment (Positive/ Negative)

```{r}
# analyze the mood 

sentiments_bing <- get_sentiments("bing")

sentiment_analysis_bing <- german_lyrics_cleaned %>%
  inner_join(sentiments_bing, by = "word") %>%
  count(sentiment, sort = TRUE)

# distribution positive /negative Words
sentiment_analysis_bing

ggplot(sentiment_analysis_bing, aes(x = sentiment, y = n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Positive & Negative Sentiments in Song Lyrics", x = "Sentiment", y = "Count")

```

The sentiment analysis of the song lyrics shows that negative words occur significantly more frequently than positive ones. This could indicate that the song lyrics tend to deal with melancholic, critical or gloomy topics.

#### NRC Sentiment Anaylysis

```{r}
sentiments_nrc <- get_sentiments("nrc")

# calculate emotions freqnecies
sentiment_analysis_nrc <- german_lyrics_cleaned %>%
  inner_join(sentiments_nrc, by = "word") %>%
  count(sentiment, sort = TRUE)


ggplot(sentiment_analysis_nrc, aes(x = reorder(sentiment, -n), y = n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Emotional Analysis of songs", x = "Emotions", y = "Frequencies")


```

The emotional analysis of the lyrics shows that negative emotions occur most frequently, followed by fear and a moderate number of positive terms. This indicates that the lyrics often have a gloomy or serious atmosphere, but still contain elements of trust and positive emotions.

#### Word Correlations: Male & Female

```{r}

# word correlations
word_correlation <- german_lyrics_cleaned %>%
  unnest_tokens(word, lyrics) %>%
  pairwise_cor(word, track_name, sort = TRUE)

# masculine and feminine terms
male_terms <- c("digga")
female_terms <- c("frau'n")

# words that correlate with masculine terms
male_related_words <- word_correlation %>%
  filter(item1 %in% male_terms | item2 %in% male_terms) %>%
  mutate(
    male_term = ifelse(item1 %in% male_terms, item1, item2),
    other_term = ifelse(item1 %in% male_terms, item2, item1)
  ) %>%
  filter(!(other_term %in% male_terms)) %>%
  filter(correlation > 0.1) %>%
  arrange(desc(correlation)) %>%
  head(20)

# words that correlate with feminine terms
female_related_words <- word_correlation %>%
  filter(item1 %in% female_terms) %>%
  mutate(
    female_term = ifelse(item1 %in% female_terms, item1, item2),
    other_term = ifelse(item1 %in% female_terms, item2, item1)
  ) %>%
  filter(!(other_term %in% female_terms)) %>%
  filter(correlation > 0.1) %>%
  arrange(desc(correlation)) %>%
  head(20)

# visualization of correlations for male-related terms
ggplot(male_related_words, 
       aes(x = reorder(other_term, correlation), y = correlation)) +
  geom_col(fill = "#6699FF") +
  coord_flip() +
  theme_minimal() +
  labs(
    title = "Words Associated with Male Terms in German Lyrics",
    x = "Associated Words", 
    y = "Correlation Strength"
  )

# visualization of correlations for female-related terms
ggplot(female_related_words, 
       aes(x = reorder(other_term, correlation), y = correlation)) +
  geom_col(fill = "#FF6699") +
  coord_flip() +
  theme_minimal() +
  labs(
    title = "Words Associated with Female Terms in German Lyrics",
    x = "Associated Words", 
    y = "Correlation Strength"
  )


```

Male-Associated Words: The words most correlated with male-related terms in German lyrics include "Wien" (Vienna), "ruf" (call), "krieg" (war), "anzug" (suit), and "Mercedes." These words suggest themes related to power, status, and action, which are often associated with masculinity in lyrical contexts.

Female-Associated Words: The words most correlated with female-related terms include "vorbild" (role model), "schlechtes" (bad), "richtig" (right), and "freund" (friend). These associations indicate a mix of both positive and negative connotations, reflecting diverse representations of women in lyrics.

The words associated with male terms in german lyrics change each time we run our code, so our analysis may vary.

#### Word Correlations

```{r}

word_correlation <- german_lyrics_cleaned %>%
  unnest_tokens(word, lyrics) %>%
  pairwise_cor(word, track_name, sort = TRUE)


print(head(word_correlation, 20))

word_correlation

# Filter für "Mann"
mann_correlation <- word_correlation %>%
  filter(item1 == "männer" | item2 == "mann")

print(mann_correlation)

# Filter für "Frau"
frau_correlation <- word_correlation %>%
  filter(item1 == "frauen"| item2 == "frauen")

print(frau_correlation)

```

### Turkish Word Frequencies & Sentiment Analysis 

```{r}
#| warning: false
#| include: false
word_freq <- dfm_text |> 
  convert(to = "data.frame") |> 
  gather(key = "word", value = "frequency") |> 
  filter(frequency > 0) |> 
  arrange(desc(frequency)) |> 
  mutate(frequency = as.numeric(frequency)) |>
  filter(!is.na(frequency)) 
  


word_freq <- word_freq |> 
  slice(-1:-15) |> 
  filter(!word %in% turkish_stops) |> 
  filter(!word %in% c("bi", "mi", "he", "senle", "benle", "şeyini", "neydi", "çoksöyle"))

  print(word_freq)
```

#### Bing Sentiment Analysis (Positive/ Negative)

```{r}
# Load Bing sentiment lexicon
sentiments_bing_tr <- get_sentiments("bing")

# Perform sentiment analysis using Bing lexicon
sentiment_analysis_bing_tr <- top_artists_tracks_tr_atomic %>%
  unnest_tokens(word, lyrics) %>%  # Tokenize lyrics
  filter(!word %in% turkish_stops) %>%  # Remove stopwords
  inner_join(sentiments_bing_tr, by = "word") %>%  # Join sentiment lexicon
  count(sentiment, sort = TRUE)  # Count occurrences of positive/negative words

# View results
print(sentiment_analysis_bing_tr)

# Plot positive vs. negative sentiment
ggplot(sentiment_analysis_bing_tr, aes(x = sentiment, y = n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Positive & Negative Sentiments in Turkish Lyrics", x = "Sentiment", y = "Count")

```

#### NRC Sentiment Analysis

```{r}
sentiments_nrc <- get_sentiments("nrc")

sentiment_analysis_nrc <- top_artists_tracks_tr_atomic %>%
  unnest_tokens(word, lyrics) %>%  # Tokenize the lyrics to get individual words
  filter(!word %in% turkish_stops) %>%  # Exclude stopwords
  inner_join(sentiments_nrc, by = "word") %>%
  count(sentiment, sort = TRUE)  # Count instances of each sentiment

# Show the counts of emotions
print(sentiment_analysis_nrc)

```

```{r}

ggplot(sentiment_analysis_nrc, aes(x = reorder(sentiment, n), y = n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  theme_minimal() +  # Use a minimal theme for better aesthetics
  labs(title = "Emotion Analysis of Turkish Lyrics", x = "Emotion", y = "Frequency") +
  coord_flip()
```


#### Word Correlation Analysis

Turkish rap-hiphop songs like to refer to men in the context of love and material concepts such as money and cars ('para' = money, 'vito' = famous car model vito). It also stresses the word 'corleone' - which is a known name for many of us - that requires no explanation.

It mostly talks about men who like to have fun in parties (see 'partilerde' = 'at parties', 'oynuyom' = 'I dance' or 'I play', 'ışklar' = 'lights', and 'tavlıyon' = 'you pull girls'). Funny, right!!

As all the artists from our Turkish playlist are men, it is appropriote to say that male rappers refer to women in melancholic contexts, highlighted by words such as 'uyuyamamak' (to not be able to sleep), 'karmakarışık' (very complicated), 'geceler, geceleri, geceleyin' (at night), 'fıttırırken' (as I go crazy), 'duygularım' (my emotions), 'acımasız' (cruel), 'bira' (beer). They also referred to women in the context of fun, although not quite prominently, stressed by 'eğlence' (fun).

```{r}
word_correlation_tr <- top_artists_tracks_tr_atomic %>%
  filter(!is.na(track_name)) %>%
  unnest_tokens(word, lyrics) %>%
  filter(!word %in% turkish_stops, nchar(word) > 2) %>%
  pairwise_cor(word, track_name, sort = TRUE)

male_terms_tr <- c("adam", "lavuk", "eleman", "piç", "çocuk", "herif", "dallama")

# words that correlate with masculine terms
male_related_words_tr <- word_correlation_tr %>%
  filter(item1 %in% male_terms_tr | item2 %in% male_terms_tr) %>%
  mutate(
    male_term = ifelse(item1 %in% male_terms_tr, item1, item2),
    other_term = ifelse(item1 %in% male_terms_tr, item2, item1)
  ) %>%
  filter(!(other_term %in% male_terms_tr)) %>%
  filter(correlation > 0.1) %>%
  arrange(desc(correlation)) %>%
  head(20)


ggplot(male_related_words_tr, 
       aes(x = reorder(other_term, correlation), y = correlation)) +
  geom_col(fill = "#6699FF") +
  coord_flip() +
  theme_minimal() +
  labs(
    title = "Words Associated with Male Terms in Turkish Lyrics",
    x = "Associated Words", 
    y = "Correlation Strength"
  )


female_terms_tr <- c("kadın", "kadınlar", "o", "kız", "anne", "kızım", 
                     "eş", "kız kardeş", "abla", "gelin", "aşk")

female_related_words_tr <- word_correlation_tr %>%
  filter(item1 %in% female_terms_tr | item2 %in% female_terms_tr) %>%
  mutate(
    female_term = ifelse(item1 %in% female_terms_tr, item1, item2),
    other_term = ifelse(item1 %in% female_terms_tr, item2, item1)
  ) %>%
  filter(!(other_term %in% female_terms_tr)) %>%
  filter(correlation > 0.1) %>%
  arrange(desc(correlation)) %>%
  head(20)  # Focus on top 20 correlations

ggplot(female_related_words_tr, 
       aes(x = reorder(other_term, correlation), y = correlation)) +
  geom_col(fill = "#FF9999") +
  coord_flip() +
  theme_minimal() +
  labs(
    title = "Words Associated with Female Terms in Turkish Lyrics",
    x = "Associated Words", 
    y = "Correlation Strength"
  )

```

#### AFINN Sentiment Analysis

```{r}
# Load AFINN lexicon
sentiments_afinn_tr <- get_sentiments("afinn")

# Perform sentiment analysis on Turkish lyrics
sentiment_analysis_afinn_tr <- top_artists_tracks_tr_atomic %>%
  unnest_tokens(word, lyrics) %>%
  filter(!word %in% turkish_stops) %>%
  inner_join(sentiments_afinn_tr, by = "word") %>%
  summarise(sentiment_score = sum(value, na.rm = TRUE))  # Aggregate sentiment scores

# View results
print(sentiment_analysis_afinn_tr)
```

### Spanish Word Frequencies & Sentiment Analysis 

#### Bing Sentiment Analysis (Positive/ Negative)

```{r}
sentiments_bing_es <- get_sentiments("bing")

sentiment_analysis_bing_es <- top_artists_tracks_es_atomic %>%
  unnest_tokens(word, lyrics_es) %>%
  filter(!word %in% all_stopwords) %>%
  inner_join(sentiments_bing_es, by = "word") %>%
  count(sentiment, sort = TRUE)  

print(sentiment_analysis_bing_es)

ggplot(sentiment_analysis_bing_es, aes(x = sentiment, y = n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Positive & Negative Sentiments in Spanish Lyrics", x = "Sentiment", y = "Count")

```

#### NRC Sentiment Anaylysis 

```{r}
sentiments_nrc_es <- get_sentiments("nrc")

# emotion analysis
sentiment_analysis_nrc_es <- top_artists_tracks_es_atomic %>%
  unnest_tokens(word, lyrics_es) %>%
  filter(!word %in% all_stopwords) %>%
  inner_join(sentiments_nrc_es, by = "word") %>%
  count(sentiment, sort = TRUE)  # occurrences of each emotion

print(sentiment_analysis_nrc_es)

# visualize emotion distribution
ggplot(sentiment_analysis_nrc_es, aes(x = reorder(sentiment, -n), y = n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Emotional Analysis of Spanish Lyrics", x = "Emotion", y = "Frequencies")

```

#### Word Correlations: Male 

```{r}
spanish_stopwords <- stopwords::stopwords("es")

word_correlation_es <- top_artists_tracks_es_atomic %>%
  filter(!is.na(track_name_es)) %>%
  unnest_tokens(word, lyrics_es) %>%
  filter(!word %in% spanish_stopwords, nchar(word) > 2) %>%
  pairwise_cor(word, track_name_es, sort = TRUE)


male_terms_es <- c("hombre", "hombres", "tipo", "jefe", "rey", "bro", "pana", 
                   "gánster", "calle", "mafioso", "boss",  
                   "bandolero", "real g", "maleante", "hermano", "primo", "papi", "compa", "negocio", "lealtad", "respeto")

male_related_words_es <- word_correlation_es %>%
  filter(item1 %in% male_terms_es | item2 %in% male_terms_es) %>%
  mutate(
    male_term = ifelse(item1 %in% male_terms_es, item1, item2),
    other_term = ifelse(item1 %in% male_terms_es, item2, item1)
  ) %>%
  filter(!(other_term %in% male_terms_es)) %>%
  filter(correlation > 0.1) %>%
  arrange(desc(correlation)) %>%
  head(20)


ggplot(male_related_words_es, 
       aes(x = reorder(other_term, correlation), y = correlation)) +
  geom_col(fill = "#6699FF") +
  coord_flip() +
  theme_minimal() +
  labs(
    title = "Words Associated with Male Terms in Spanish Lyrics",
    x = "Associated Words", 
    y = "Correlation Strength"
  )

# a focused list of female-related words in Spanish
female_terms <- c("mujer", "mujeres", "ella", "chica", "madre", "niña", 
                  "señora", "esposa", "novia", "hermana", "hija")

# words correlated with female terms
female_related_words <- word_correlation_es %>%
  filter(item1 %in% female_terms | item2 %in% female_terms) %>%
  # correlations between female terms and other words
  mutate(
    female_term = ifelse(item1 %in% female_terms, item1, item2),
    other_term = ifelse(item1 %in% female_terms, item2, item1)
  ) %>%
  filter(!(other_term %in% female_terms)) %>%
  filter(correlation > 0.1) %>%
  arrange(desc(correlation)) %>%
  head(20)  # 

ggplot(female_related_words, 
       aes(x = reorder(other_term, correlation), y = correlation)) +
  geom_col(fill = "#FF9999") +
  coord_flip() +
  theme_minimal() +
  labs(
    title = "Words Associated with Female Terms in Spanish Lyrics",
    x = "Associated Words", 
    y = "Correlation Strength"
  )
```

### AFINN Sentiment Analysis (Numerical Scores)

```{r}
sentiments_afinn_es <- get_sentiments("afinn")

sentiment_analysis_afinn_es <- top_artists_tracks_es_atomic %>%
  unnest_tokens(word, lyrics_es) %>%
  filter(!word %in% all_stopwords) %>%
  inner_join(sentiments_afinn_es, by = "word") %>%
  summarise(sentiment_score = sum(value, na.rm = TRUE))  

print(sentiment_analysis_afinn_es)

```

## DE- TR- ES Sentiment Comparison

```{r}
sentiment_analysis_bing_es <- sentiment_analysis_bing_es %>% mutate(language = "Spanish")
sentiment_analysis_bing_tr <- sentiment_analysis_bing_tr %>% mutate(language = "Turkish")
sentiment_analysis_bing_de <- sentiment_analysis_bing %>% mutate(language = "German")

sentiment_comparison <- bind_rows(sentiment_analysis_bing_es, 
                                  sentiment_analysis_bing_tr, 
                                  sentiment_analysis_bing_de)

sentiment_analysis_nrc_es <- sentiment_analysis_nrc_es %>% mutate(language = "Spanish")
sentiment_analysis_nrc_tr <- sentiment_analysis_nrc %>% mutate(language = "Turkish")
sentiment_analysis_nrc_de <- sentiment_analysis_nrc %>% mutate(language = "German")

emotion_comparison <- bind_rows(sentiment_analysis_nrc_es, 
                                sentiment_analysis_nrc_tr, 
                                sentiment_analysis_nrc_de)
```

The below bar plot provides a quick comparison for all three languages on the basis of positive and negative sentiments. Due to considerably greater volume of words in the songs that are present in our list, German tops both sentiments in the count of words that represent each sentiment.

Spanish is second to German in terms of the count of words reflecting both positivity and negativity, however, both sentiments post highly close numbers, offering a balance as explained in the previous sections.

Turkish has the lowest number of words in both sentiments, however, this is due to the relatively lower volume of words across all songs. This also has implications that Turkish rap-hiphop songs are not constructed in sentences with a high number of words, instead, they form shorter sentences and let the vibes do the rest!

It is also possible to say that German rap/hiphop is arguably based on long sentences and maybe even story telling, just like old school versions of the genre. Gür likes this a lot!

Spanish songs, on the other hand, demonstrate an in-between performance regarding the number of words, proposing a modest way.

```{r}
ggplot(sentiment_comparison, aes(x = sentiment, y = n, fill = language)) +
  geom_bar(stat = "identity", position = "dodge") +  
  theme_minimal() +
  labs(title = "Comparison of Positive & Negative Sentiments Across Languages",
       x = "Sentiment Type", y = "Count") +
  scale_fill_manual(values = c("Spanish" = "#F1BF00", "Turkish" = "#C8102E", "German" = "black")) +
  theme(legend.title = element_blank())  
```

```{r}
ggplot(emotion_comparison, aes(x = reorder(sentiment, -n), y = n, fill = language)) +
  geom_bar(stat = "identity", position = "dodge") +  
  theme_minimal() +
  labs(title = "Comparison of Emotional Sentiments Across Languages",
       x = "Emotion", y = "Frequency") +
  scale_fill_manual(values = c("Spanish" = "#F1BF00", "Turkish" = "#C8102E", "German" = "black")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.title = element_blank()) 
```
